### 2016-08-28 paper.tex
Fix virtual camber reference

The tendency of $C_P$ to continue increasing slightly could be an effect of flow
curvature---caused by the finite $c/R$---which imparts a ``virtual camber''
\cite{Migliore1980}, or can be thought of as producing a ``lead'' in angle of
attack since cambered airfoils have non-zero lift at zero angle of attack
\cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
$Re$-independence of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.

>>>>

The tendency of $C_P$ to continue increasing slightly could be an effect of flow
curvature---caused by the finite $c/R$---which imparts a ``virtual camber''
\cite{Migliore1980}, or can be thought of as producing a ``lead'' in angle of
attack since cambered airfoils have non-zero lift at zero angle of attack
\cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
$Re$-independence of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-Energies}.
